Crowdy: Social Crowd Visualization

### 2011-04-26 docs/crowdy_gui.tex
Added feature in search to support searching by minimum value of clustering coefficient

\section{Evaluation}

\section{CONCLUSIONS}
In conclusion, we have implemented the Social Crowd Visualization system as a web application that enable users to visualize,summarize and organize temporal crowd formation on Twitter. We studied several types of potential users and design the interface carefully to meet their needs. We implemented a few different layout format and a search component to ease the crowd retrieval effort on user. Finally, we design a sequence of possible evaluations for this system. The interface will be continually improved as it is also an on-going DARPA project with the InfoLab. As the next step, a few direction such as user model construction and map view implementation will be carried out.
\section{FUTURE WORK}

>>>>

\section{Evaluation Plan}
In order to evaluate our system, we planned to conduct a 2-step usability study
which includes a pilot study, and an evaluation study. In the pilot study, we
will ask a relative small number of users (e.g., 5 - 10 people) to try our
system, and fill in the usability questionaire. Then, we will refine the system
based on the feedbacks from the pilot study (i.e., fixing bugs reported by users,
modifying featuers that were not preferred). Finally, a large scale evaluation
study also in the form of questionaire will be conducted on a user base of 30 -
50 users including three types of users we mentioned earlier: normal users, 
Twitter users, and analysts. The refinement step and the large-scale detailed
evaluation study will be generated after the step of the pilot study. Thus, in
this report, we only focus on the design of the pilot study.

\subsection{Pilot Study}

The pilot study we propose contains XX 5-scale likert (i.e., very good, good,
okay, bad, and very bad) questions, and YY open questions. The questions are
listed below:

\begin{itemize}
\item Whether the interface for timeline view is easy to use?
\item Whether the interface for list view is easy to use?
\item Whether the search feature for timeline view is easy to use?
\item Whether the search results in the timeline view could answer the information
need for your query.
\item Whether the search feature for list view is easy to use?
\item Whether the search results in the list view could answer the information
need for your query.
\item Whether 
\end{itemize}

\section{CONCLUSIONS}
In conclusion, we have implemented the Social Crowd Visualization system as a
web application that enable users to visualize,summarize and organize temporal
crowd formation on Twitter. We studied several types of potential users and
design the interface carefully to meet their needs. We implemented a few
different layout format and a search component to ease the crowd retrieval
effort on user. Finally, we design a sequence of possible evaluations for this
system. The interface will be continually improved as it is also an on-going
DARPA project with the InfoLab. As the next step, a few direction such as user
model construction and map view implementation will be carried out.

\section{FUTURE WORK}
